Dynein walks like an Imperial AT-ST

### 2017-10-16 reorganize/papers/paper/paper.tex
minor changes to paper.

\dropcap{D}ynein is a motor protein used to generate directed force in cells. The protein is a homodimer which binds to cellular filaments known as microtubules (MTs). Each monomer uses ATP hydrolysis to step along the MT. ... \\

Compared to other motors kinesin and myosin, dynein is unique in that it has a widely varied step size. Dynein's average step is 8nm in the forwards direction, but it is capable of taking 32nm steps in the forwards and reverse directions \cite{weihongpaper} \cite{yildizpaper}.

@@

Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.
Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.

>>>>

\dropcap{D}ynein is a motor protein used to generate directed force in cells. The protein is a homodimer which binds to cellular filaments known as microtubules (MTs). Each monomer has several ATPase domains arranged in a larger globular domain known as the head. This head is the site which hydrolyzes ATP and undergoes the conformational changes responsible for dynein's step. The head is attached via a long chain to the microtubule binding domain (MTBD). Dynein is an interesting structure in that it manages to coordinate ATPase chemistry at its head with MT-releasing chemistry at its MTBD, some 20nm away \cite{mt-atp-coupling}. The head has a long tail domain coming off it, which eventually dimerizes to the other monomer.\\

Dynein is unique in that it has a widely varied step size. Dynein's average step is 8 \textit{nm} in the forwards direction, but it is capable of taking 32 \textit{nm} steps in the forwards and reverse directions \cite{weihongpaper} \cite{yildizpaper}. This stochastic, varied stepping is contrasted with the much more regular 8 \textit{nm} step size of kinesin, another bipedal motor protein \cite{kinesin-step-size}. It has been suggested that dynein's long separation between its head

Dynein is known to change stepping behavior and direction as a response to forwards or backwards load \cite{responsetoload}.

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris in aliquet quam, a cursus orci. Fusce vitae faucibus tortor, vel molestie nibh. Proin condimentum cursus mollis. Praesent euismod ligula sit amet libero elementum, sed commodo velit suscipit. Integer sed nisl vitae nibh dapibus sagittis. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Nullam et semper sem. Nulla fringilla lacus quis justo tincidunt venenatis. Vestibulum aliquet ante diam, nec accumsan augue rutrum id. Nam sollicitudin magna vitae mauris pellentesque, et rhoncus felis accumsan.\\

Etiam ullamcorper elit a interdum molestie. Phasellus aliquam nulla nec orci sodales, sit amet bibendum odio pulvinar. Nullam at pulvinar lectus. Nulla facilisi. Phasellus ut magna ut nunc vehicula posuere non ac ligula. Nulla facilisi. Duis ultrices ornare turpis, eget tempus mauris pulvinar interdum.\\

Curabitur eget nisi tellus. Nullam bibendum et dolor et rutrum. Sed tincidunt quam nec laoreet tincidunt. Etiam quam erat, tempus in posuere eget, pellentesque vel ex. Nunc non turpis sagittis, condimentum ante porttitor, pulvinar risus. Proin sodales, odio vel efficitur porta, nunc ligula ornare leo, ut lobortis elit ante bibendum mauris. Sed molestie nisl at elit efficitur interdum.\\

Nam ultricies efficitur nunc, in tristique tellus auctor vitae. Aliquam ante leo, varius a ante sit amet, pretium efficitur elit. Nulla suscipit, nunc eget mollis blandit, nulla lorem venenatis ipsum, lobortis ultricies leo justo eu diam. Proin fringilla, purus non hendrerit vulputate, eros est ultrices massa, vel faucibus mi risus ac magna. Ut varius justo maximus finibus aliquam. Nullam rutrum vestibulum eros sed accumsan. Vestibulum a porttitor urna, porttitor tempus sem. Quisque dapibus aliquam pulvinar. Fusce vehicula nisl a tellus semper vulputate.\\

Nunc lobortis, tellus sit amet interdum maximus, justo elit faucibus turpis, quis volutpat magna lorem id purus. Donec urna erat, semper non egestas eget, sodales at quam. Etiam interdum tincidunt purus, eu tempor mauris consequat consequat. Aenean feugiat sapien enim, et cursus sem ultrices vitae. Vivamus enim purus, malesuada sit amet turpis sed, porta consequat tellus. Orci varius natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aenean vitae nisl convallis, venenatis magna et, aliquet sem. Proin diam est, rutrum at auctor vel, gravida nec magna. Aliquam erat volutpat. Nunc eu tempus ex. Praesent eget aliquam metus, ut faucibus sapien. Donec porttitor, dolor et accumsan volutpat, est neque sagittis libero, eu lobortis lacus lorem sed diam.\\
